### 2024-04-23 texts/paper_closing.tex
some more notes which need to be written out

% Created 2024-04-22 ma 19:57
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

In recent years, private collector-run museums have seen an unprecedented proliferation, with hundreds of organizations founded since the beginning of the millenium \parencite{Velthuis_etal_2023_boom,LarrysList_2015_report}.
These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
While the emergence of this organizational form has attracted attention (cf. \cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
In this paper, I address this gap by investigating the closure event of members of this new organizational form.
This exercise does not only provide insights into private museums in particular, but also more generally into processes of organizational identity, especially regarding legitimation and reputation.

@@

The empirical record of the link between identity and survival for non-profit organizations is mixed: 
For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close.
However, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Understandability \parencite{Glynn_Abzug_2002_names} might thus be limited if an organization is atypical \parencite{Rosch_1975_family}, i.e. displays an unusual combination of features.
In the case of private museums, such cases might be combinations of features from house museums (e.g. accessibility only by appointment) with full-service museums (e.g. extensive activities). 
Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Apr 19 19:04:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 22 19:37:32 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyr}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .16 \; (0.37) & .16 \; (0.37) \\ 
   & Gender - Couple & .20 \; (0.36) & .13 \; (0.37) \\ 
   & Founder died & -.06 \; (0.57) & -.02 \; (0.56) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .93 \; (0.49) & .83 \; (0.48) \\ 
   & Self-Identification - Collection & .34 \; (0.59) & .36 \; (0.59) \\ 
   & Self-Identification - Other & 1.45 \; (0.39)^{***} & 1.38 \; (0.39)^{***} \\ 
   & AN Ranking - Included & .26 \; (0.38) & .22 \; (0.38) \\ 
   & AN Ranking - Dropped & .81 \; (0.51) & .66 \; (0.52) \\ 
   & Founder name in Museum name & -.44 \; (0.33) & -.42 \; (0.33) \\ 
   & Exhibition any & .13 \; (0.33) &  \\ 
   & Exhibition any last 5 years &  & .39 \; (0.32) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & Time Period 2005-2009 &  & .40 \; (1.16) \\ 
   & Time Period 2010-2014 &  & 1.28 \; (1.04) \\ 
   & Time Period 2015-2019 &  & 1.43 \; (1.03) \\ 
   & Time Period 2020-2024 &  & 1.51 \; (1.05) \\ 
   & PM density (country) & .63 \; (0.45) & .52 \; (0.51) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .32 \; (0.11)^{**} & .30 \; (0.12)^{**} \\ 
   & Nbr PM within 10km & .29 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} & -.09 \; (0.04)^{**} \\ 
   \hline
 & Museum-years & 5862 & 5862 \\ 
   & Closures & 51 & 51 \\ 
   & log. Likelihood & -246.02 & -241.64 \\ 
   & AIC & 522.03 & 521.28 \\ 
   & BIC & 551.01 & 557.99 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-04-23 di 20:31
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

In recent years, private collector-run museums have seen an unprecedented proliferation, with hundreds of organizations founded since the beginning of the millenium \parencite{Velthuis_etal_2023_boom,LarrysList_2015_report}.
These museums, run by individual collectors, constitute an addition to established organizational forms of art provision such as museums operated and financed by the state, foundations or associations.
While the emergence of this organizational form has attracted attention (cf. \cite{Kolbe_etal_2022_privatemuseum} for a literature review), the process of closure has received considerably less attention.
In this paper, I address this gap by investigating the closure event of members of this new organizational form.
Analysis which factors are associated with museum closures provides insight not only into the event of closing, but also into the ongoing processes of a private museums, such as dependency relationships.
Furthermore, analyzing which museums survive allows to make informed speculations on the future of this recently emerged organizational form.

\subsection*{private museum 3 crisis}

Museums, including private museums, might be relatively resilient \cite{Geller_Salamon_2010_resilience}: 
tightening belt, fundraising, entrepreneurial strategies, downsizing
The form of museums also implies commitment of resources, larger than that of other NPOs, which in turn provides capabilities, e.g. staff that is able to search for alternative revenue sources.

\subsection*{Private museums relationships}

A private museum is entangled in a number of dependencies.
A crucial one is the relationship to the founder, without whom the private museum would not exist.
Founders often control some aspects of management/operations.
While the exact power relationships within museums are hard to observe due to the lack of transparency, which makes it in particular to assess the role of third parties, it is plausible to assume that they cannot exist against the wishes of the founder.
Next to exhibiting the founder's collection, they likely also to a large extent dependent on continued financial contributions of the founder, as museums are chronically unprofitable (which is evidenced by their high share of NPOs or publicly owned/run museums, rather than for-profit companies). 
While the lack of transparency again makes it hard to systematically assess the financial importance of founder contributions to the existence of museums, \textbf{anecdotal} evidence suggests it to be substantial \parencite{Velthuis_Gera_forthcoming_fragility}.

Furthermore, private museums, as (non-profit) organizations, is deeply entangled with its environment.
Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
While some of these aspects can be influenced by the founder (in particular the available audience, via being able to decide a location and the extent to which a museum should organize exhibitions), other are less so.
In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
The image that these parties have of the private museum might be substantial importance in guiding their decision-making.

@@

The empirical record of the link between identity and survival for non-profit organizations is mixed: 
For example \textcite{Bielefeld_1994_survival} finds that NPOs who pursue less legitimation strategies (obtaining endorsements, lobbying or contributing to local causes) are more likely to close.
However, other studies find limited impact of legitimacy on survival, both when measured via density \parencite{Bogaert_etal_2014_ecological} or from archival sources and interviews \parencite{Fernandez_2007_dissolution}.
Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, it is generally not subject to state regulation), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited "devaluation" of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 17:09:14 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 1.5e-01 &   0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 20:19:31 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .16 \; (0.37) \\ 
   & Gender - Couple & .17 \; (0.36) \\ 
   & Founder died & -.06 \; (0.57) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .91 \; (0.49) \\ 
   & Self-Identification - Collection & .33 \; (0.59) \\ 
   & Self-Identification - Other & 1.44 \; (0.39)^{***} \\ 
   & AN Ranking - Included & .27 \; (0.38) \\ 
   & AN Ranking - Dropped & .76 \; (0.52) \\ 
   & Founder name in Museum name & -.41 \; (0.33) \\ 
   & Exhibition any & .13 \; (0.33) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .59 \; (0.46) \\ 
   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .31 \; (0.11)^{**} \\ 
   & Nbr PM within 10km & .28 \; (0.09)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
   & Great Recession (2008/09) & -1.21 \; (1.02) \\ 
   & Covid Pandemic (2020/21) & .27 \; (0.34) \\ 
   \hline
 & Museum-years & 5862 \\ 
   & Closures & 51 \\ 
   & log. Likelihood & -244.54 \\ 
   & AIC & 523.08 \\ 
   & BIC & 555.92 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
